The SMT Competition 2015--2018

### 2019-04-14 2018/report/SMT-COMP.tex
Report: Layout and clean up sat/unsat/24s tables.

%\usepackage{showframe}   % debug

@@

\colorlet{bool}{blue!10}
\colorlet{cvc4}{cyan!10}
\colorlet{smti}{yellow!10}
\colorlet{yices}{green!10}
\colorlet{vamp}{orange!10}
\colorlet{q3b}{red!10}
\colorlet{prob}{gray!10}
\colorlet{z}{Fuchsia!10}
\colorlet{coli}{Brown!10}
\colorlet{spass}{Lavender!10}
\colorlet{apr}{PineGreen!10}
\colorlet{rat}{Goldenrod!10}
\colorlet{cvc3}{GreenYellow!10}
\colorlet{redl}{Yellow!10}
\colorlet{nonc}{black!55}

@@

In the Main-track all divisions contain a mixture of problems that are satisfiable and unsatisfiable. However, some solvers may be specialised or optimised for a particular kind of problem. Therefore, it is interesting to ask whether the winners of divisions might have changed if benchmarks in that division had been restricted to one of these results. Table~\ref{tab:results:sat:unsat} shows the changes in division winners if only satisfiable or unsatisfiable results are given. This table only lists a solver if the winner has changed. A non-competing solver is listed by itself if it now outperforms the winning competitive solver.

@@

\begin{table}
\caption{Alternative winners if only Satisfiable (top) or Unsatisfiable (bottom) benchmarks had been considered. These results are in reference to those given in Table~\ref{tab:winners-main}.\label{tab:results:sat:unsat}}
\centering
\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
\toprule
Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
\hline \hline
ALIA    &   &   &   & Alt-Ergo  \\
AUFLIA  & CVC3  &   &   & Alt-Ergo  \\
AUFLIRA &   & CVC4  & CVC4  & Alt-Ergo  \\
AUFNIRA & \nc{Z3}  & CVC4 \nc{Z3}  & CVC4 \nc{Z3}  & \nc{Z3}  \\
BV      &   & \nc{Z3}  & Boolector  & Boolector  \\
LRA     &   &   & veriT+Redlog  &   \\
NIA     & CVC3  &   &   &   \\
NRA     & CVC3  & CVC4  & CVC4  & CVC4 \nc{Z3}  \\
QF\_ABV  &   & Yices2  & Yices2  &   \\
QF\_AUFBV        & Yices  & Yices2  &   & Yices2  \\
QF\_BV   &   & \nc{Z3}/MinkeyRink  &   &   \\
QF\_FP   &   &   &   & CVC4  \\
QF\_LIA  & \nc{Z3}  &   &   &   \\
QF\_LRA  &   &   & Yices2  & Yices2  \\
QF\_NIA  &   & SMT-RAT  &   &   \\
QF\_NIRA &   &   & CVC4  &   \\
QF\_NRA  &   &   & \nc{Z3}  &   \\
QF\_UFBV &   &   &   & Yices2  \\
QF\_UFIDL        & \nc{Z3}  & \nc{Z3}  & \nc{Z3}  & \nc{Z3} veriT  \\
QF\_UFNIA        & CVC3  &   & CVC4  &   \\
UF      &   & Vampire  &   & Vampire/-  \\
UFBV    &   & Boolector  &   &   \\
UFDTLIA &   &   & CVC4  &   \\
UFLIA   & \nc{Z3}  &   &   &   \\
UFLRA   & CVC3  & CVC4  &   &   \\
UFNIA   &   & CVC4  & CVC4  & CVC4  \\
\bottomrule
\end{tabular}

\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
\toprule
Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
\hline \hline
BV      &   & CVC4  &   &   \\
NIA     &   & CVC4  & Vampire  & Vampire  \\
QF\_AUFBV        &   &   & CVC4  &   \\
QF\_AUFNIA       & \nc{Z3}  & \nc{Z3}  &   &   \\
QF\_BV   &   &   & Boolector  &   \\
QF\_IDL  & CVC4  &   & \nc{Z3}  & CVC4 \nc{Z3}  \\
QF\_LIA  & SMTInterpol  & SMTInterpol  & SMTInterpol  & SMTInterpol  \\
QF\_NIA  & CVC3  &   & Yices2  &   \\
QF\_NRA  &   &   &   & CVC4  \\
QF\_UFLIA        &   &   & \nc{Z3}  &   \\
QF\_UFNRA        &   & CVC4 \nc{Z3}  & CVC4  & CVC4 \nc{Z3}  \\
UF      &   &   & CVC4  & -/CVC4  \\
UFIDL   &   & Vampire \nc{Z3}  & \nc{Z3}  &   \\
UFLRA   &   &   & veriT  & veriT  \\
\bottomrule
\end{tabular}

\end{table}

@@

\begin{table}
\caption{Alternative winners if the time limit had been 24 seconds.\label{tab:results:24s}}
\centering

\begin{tabular}{r@{\hskip 1em}>{\columncolor[gray]{.95}[.25em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][.5em]}c@{\hskip 1em}>{\columncolor[gray]{.95}[.5em][0.25em]}c}
\toprule
Division         &  2015                 &  2016                    &  2017                  &  2018                      \\
\hline \hline
AUFLIA  &   & Vampire \nc{Z3}  & veriT  &   \\
AUFLIRA & CVC3  &   &   & -/Alt-Ergo  \\
AUFNIRA & \nc{Z3}  &   &   & \nc{Z3}  \\
BV      &   &   &   & Boolector/Boolector \nc{Z3}  \\
NRA     &   &   &   & CVC4/CVC4 \nc{Z3}  \\
QF\_ABV  &   & Yices2  &   &   \\
QF\_ANIA &   & \nc{Z3}  & \nc{Z3}  &   \\
QF\_BV   & CVC4  & STP \nc{Z3}  & Boolector+CaDiCaL/-  & Boolector  \\
QF\_LIA  & Yices  & Yices2  & Yices2  &   \\
QF\_LRA  & Yices  & Yices2  & Yices2  & Yices2  \\
QF\_NIA  &   &   & Yices2  & Yices2  \\
QF\_NIRA &   &   & Yices2 \nc{Z3}  & Yices2 \nc{Z3}  \\
QF\_NRA  &   &   & \nc{Z3}  &   \\
QF\_UF   & veriT  & veriT  &   &   \\
QF\_UFNRA        &   & CVC4 \nc{Z3}  & CVC4  & \nc{Z3}  \\
UF      &   & Vampire  &   &  Vampire/- \\
UFBV    &   & Boolector  &   &   \\
UFIDL   &   & Vampire \nc{Z3}  & \nc{Z3}  &   \\
UFLIA   &   &   &   & \nc{Z3}  \\
UFLRA   &   &   & veriT  & veriT  \\
UFNIA   & \nc{Z3}  &   &   & CVC4/\nc{Z3}  \\
\bottomrule
\end{tabular}
\end{table}

>>>>

\usepackage{showframe}   % debug

@@

\colorlet{bool}{blue!10}
\colorlet{cvc4}{cyan!10}
\colorlet{smti}{yellow!10}
\colorlet{yices}{green!10}
\colorlet{vamp}{orange!10}
\colorlet{q3b}{red!10}
\colorlet{prob}{gray!10}
\colorlet{z}{Fuchsia!10}
\colorlet{coli}{Brown!10}
\colorlet{spass}{Lavender!10}
\colorlet{apr}{PineGreen!10}
\colorlet{rat}{Goldenrod!10}
\colorlet{cvc3}{Melon!10}
\colorlet{redl}{Yellow!10}
\colorlet{alt}{LimeGreen!10}
\colorlet{verit}{MidnightBlue!10}
\colorlet{stp}{Fuchsia!10}
\colorlet{nonc}{black!55}

@@

In the Main-track all divisions contain a mixture of problems that are satisfiable and unsatisfiable. However, some solvers may be specialised or optimised for a particular kind of problem. Therefore, it is interesting to ask whether the winners of divisions might have changed if benchmarks in that division had been restricted to one of these results. Tables~\ref{tab:results:sat}-\ref{tab:results::unsat} show the changes in division winners if only satisfiable or unsatisfiable results are given. This table is in reference to Table~\ref{tab:winners-main} and only lists a solver if the result has changed. A non-competing solver is listed by itself if it was not the overall best performing solver of that division but now outperforms the winning competitive solver .

@@

\input{table-winners-main-sat-unsat}

@@

\input{table-winners-main-24s}
